---
title: "Word acquisition norms"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Word acquisition norms}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

The function `bvq_norms()` computes the proportion of children in the sample that understand or produce each item, sometimes called "word prevalence". This function returns the estimated probability of an average participant understanding or producing each word. The `bvq_norms()` function allows to condition this probability on the age, language profile or language dominance of participants, among other variables. Proportions are adjusted for zero- and one-inflation following Gelman, Hill, and Vehtari (2020).

If argument `item` is left NULL (default), proportions are computed for all items (currently `r nrow(pool)`). This may take time. If you need to compute norms for specific items, you can provide the item identifiers in the `item` argument. Available items can be consulted in the `pool` data set:

```{r pool, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)
head(pool)
```

Let's go through an example of how to use the `bvq_norms` function for a specific set of items. 

```{r responses, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)

# norms will be computed from these datasets
participants <- bvq_participants()
responses <- bvq_responses(participants = participants)

# items we want to compute norms for
my_items <- c("cat_gos", "cat_gat")

norms <- bvq_norms(
    participants = participants,
    responses = responses,
    item = my_items,
    # get data for production
    type = "produces", 
    # get data for participants aged 1 to 45 months
    age = c(1, 45), 
    # get data for bilinguals (exclude monolinguals and others)
    lp = "Bilingual"
)
```

```{r load-responses, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)
responses <- readRDS(file.path("fixtures", "responses.rds"))
participants <- readRDS(file.path("fixtures", "participants.rds"))

my_items <- c("cat_gos", "cat_gat")

norms <- bvq_norms(
    participants = participants,
    responses = responses,
    # get info from casa and abric items
    item = my_items,
    # get data for production
    type = "produces", 
    # get data for participants aged 1 to 45 months
    age = c(1, 45), 
    # get data for bilinguals (exclude monolinguals and others)
    lp = "Bilingual"
)

(norms)
```

Visualised, these data look like this:

```{r plot, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(ggplot2)

ggplot(norms, 
       aes(age, .prop,
           colour = item_dominance,
           fill = item_dominance,
           shape = item_dominance)) +
    facet_grid(~item) +
    geom_hline(yintercept = 0.5,
               linetype = "dashed") +
    geom_smooth(method = "glm", 
                method.args = list(family = "binomial"), 
                se = FALSE) +
    geom_point() +
    labs(x = "Age (months)", 
         y = "Proportion", 
         colour = "Item dominance",
         fill = "Item dominance",  
         shape = "Item dominance") +
    scale_y_continuous(limits = c(0, 1)) +
    scale_colour_manual(values = c("#003f5c", "#ff6361")) +
    theme_minimal() +
    theme(
        axis.line = element_line(colour = "black"),
        legend.position = "top",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()
    )

```
