---
title: "Word acquisition norms"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Word acquisition norms}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
data("pool", package = "bvq")
```

The function `bvq_norms()` computes the proportion of children in the sample that understand or produce each item, sometimes called **word prevalence**. This function returns the estimated probability of an average participant understanding or producing each word. The `bvq_norms()` function allows to condition this probability on the age, language profile or language dominance of participants, among other variables. Proportions are adjusted for zero- and one-inflation following Gelman, Hill, and Vehtari (2020).

If argument `item` is left NULL (default), proportions are computed for all items (currently `r format(nrow(pool), big.mark = ",")`). This may take time. If you need to compute norms for specific items, you can provide the item identifiers in the `item` argument. Available items can be consulted in the `pool` data set:

```{r pool, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)
head(pool)
```

Let's go through an example of how to use the `bvq_norms()` function for a specific set of items. 

```{r responses, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# norms will be computed from these datasets
participants <- bvq_participants()
responses <- bvq_responses(participants = participants)

# items we want to compute norms for
my_items <- c("cat_gos", "cat_gat")

norms <- bvq_norms(
    participants = participants,
    responses = responses,
    item = my_items,
    age = c(12, 35)
)
```

```{r load-responses, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)
responses <- readRDS(file.path("fixtures", "responses.rds"))
participants <- readRDS(file.path("fixtures", "participants.rds"))

my_items <- c("cat_gos", "cat_gat")

norms <- bvq_norms(
    participants = participants,
    responses = responses,
    item = my_items,
    age = c(1, 45)
)

(norms)
```

If we want to retrieve the acquisition norms of our item of interest, but also those of its translation equivalent, we can use the argument `te`. This argument can take the value `TRUE` if we want to also include the norms of the translation of the items specified in the `item` argument. For example:

```{r te-item, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
my_items <- c("cat_gos", "cat_gat")

bvq_norms(
    participants = participants,
    responses = responses,
    item = my_items,
    te = TRUE,
    age = c(15, 16)
) 
```

We can even indicate a specific translation equivalent in the `te` argument to retrieve its norms, while leaving the argument `item` blank:

```{r te, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
bvq_norms(
    participants = participants,
    responses = responses,
    te = 175,
    age = c(25, 29)
) %>% 
    filter(item_dominance=="L1")
```
