---
title: "Vocabulary sizes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vocabulary sizes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `bvq_vocabulary()` function allows to extract vocabulary sizes for individual responses to any of the questionnaires. It takes the output of the `bvq_responses()` function as an argument, and returns several measures of vocabulary size base on such dataset.

To compute vocabulary size, we first need to run `bvq_responses()` (although if this argument is not provided, `bvq_responses()` is run under the hood):

```{r responses, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)

# vocabularies will be computed from these datasets
participants <- bvq_participants()
responses <- bvq_responses(participants = participants)

bvq_vocabulary(participants, responses)
```

```{r load-responses, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)
responses <- readRDS(file.path("fixtures", "responses.rds"))
participants <- readRDS(file.path("fixtures", "participants.rds"))

(responses)
```


The `bvq_vocabulary()` computes four measures of vocabulary size.

* **Total** (`total_*`): total number of item the child was reported to know, summing both languages together.
* **L1** (`l1_*`): number of word the child was reported to know in their dominant language (e.g., Catalan words for a child whose language of most exposure is Catalan).
* **L2** (`l2_*`): number of word the child was reported to know in their non-dominant language (e.g., Spanish words for a child whose language of most exposure is Catalan)
* **Conceptual** (`concept_*`): number of concepts the child know at least one word for, regardless of the language the word belongs to.
* **TE** (`te_*`): number of translation equivalents the child knows, i.e., or how many concepts the child know one word in each language for.

Vocabulary sizes are, by default, computed in two different scales:

* **Proportion** (`*_prop`): proportion of the items the child was reported to known, from the total of items that were included in the questionnaire, and caregivers answered to.
* **Counts** (`*_count`): sum of the total number of items the child was reported to know.

The scale returned by `bvq_vocabulary()` can be modified with the `.scale` argument, which takes `"prop"` for proportions (default), and `"count"` for counts. Both can be computed using `.scale = c("prop", "count")`. For instance we can get vocabulary sizes as proportions running:

```{r props, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
bvq_vocabulary(participants, responses, .scale = "prop")
```


To get vocabulary sizes as counts, we can run this instead:

```{r counts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
bvq_vocabulary(participants, responses, .scale = "count")
```

Finally, two types of vocabulary sizes are computed:

* **Comprehension** (`understands`): number of items the child understands.
* **Production**: (`produces`) number of items the child says.

These two measures are returned in the long format under the `type` column.


## Conditional vocabulary size: the `...` extra arguments

We can also compute vocabulary sizes conditional to some variables at the item or participant level, such as semantic/functional (`semantic_category`) or language profile (`lp`), using the argument `...` argument. Just take a look at the variables included in the data frame returned by `bvq_logs()` or in the `pool` dataset. For each participant, vocabulary sizes are computed for each level or combination of levels of the variables included in the columns included in `...`. You can use this argument to preserve participant-level information in the output data frame. For instance, we can keep information about the language profile (`lp`) of the participant:

```{r by-lp, echo=TRUE, eval = FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
bvq_vocabulary(participants, responses, lp)
```

We can also can also preserve information about the items, like the semantic/functional category of the words (`semantic_category`). In this case, the vocabulary sizes will be computed for each level of the `semantic_category` variable:

```{r by-semantic-category, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
bvq_vocabulary(participants, responses, semantic_category)
```

Finally, we can preserve more than one variable, including combinations of participant-level and item-level variables, such as language profile (`lp`), age (`age`) and grammatical class (`class`):

```{r by-mult, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
bvq_vocabulary(participants, responses, age, lp, semantic_category)
```





