---
title: "Introduction to bvq"
---

The function `bvq_responses()` retrieves participants' responses to the Barcelona Vocabulary Questionnaire (BVQ) using the [formr API](https://formr.org/documentation), and returns them along participant- and item-level information. This function returns a tidy data frame in which each row is one participant's response to an individual item. 

```{r responses, eval=FALSE, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)
library(dplyr)

participants <- bvq_participants()
responses <- bvq_responses(participants)

# select relevant variables
responses %>%
    select(id, time, item, response, randomisation) %>%
    filter(!is.na(response)) # drop unanswered items
```

```{r load-responses, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(bvq)
library(dplyr)
responses <- readRDS(file.path("vignettes", "fixtures", "responses.rds"))
participants <- readRDS(file.path("vignettes", "fixtures", "participants.rds"))

(responses)
```

# Consulting participant-level information

Participant-level properties like language profile variables can be extracted using the `bvq_logs()` function.

```{r logs, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
bvq_logs(participants, responses) %>% 
    select(id, time, age, lp, starts_with("doe_"))
```

# Item properties

Item-level properties can be consulted in the `pool` data frame (see `?pool`):

```{r pool, echo=TRUE, warning=FALSE, message=FALSE}
data("pool")
pool
```

# Computing vocabulary sizes

The `bvq_vocabulary()` function allows to extract vocabulary sizes for individual responses to any of the questionnaires. It takes the output of the `bvq_responses()` function as an argument, and returns several measures of vocabulary size base on such data frame.

To compute vocabulary size, we first need to run `bvq_responses()` (although if this argument is not provided, `bvq_responses()` is run under the hood):

```{r vobcabulary, echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
bvq_vocabulary(participants, 
               responses,
               lp, # to keep participants' language profile
               .scale = "prop" # to return estimates as proportions
)
```

# Computing word acquisition norms

The function [bvq::bvq_norms()] computes the proportion of children in the sample that understand or produce each item, sometimes called **word prevalence**. This function returns the estimated probability of an average participant understanding or producing each word. The `bvq_norms()` function allows to condition this probability on the age, language profile or language dominance of participants, among other variables. Proportions are adjusted for zero- and one-inflation following Gelman, Hill, and Vehtari (2020).

```{r norms, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
# items we want to compute norms for
bvq_norms(participants,
          responses,
          item = c("cat_gos", "cat_gat"),
          age = c(12, 35)
)
```
